Stellar Bars in Isolated Gas-Rich Galaxies Do Not Slow Down

### 2022-04-08 paper/ms.tex
Small typo

After generating the gaseous disk in this way, we stitched the gas disk
together with the GALAKOS N-body disk (and bulge and dark matter halo) after
the GALAKOS disk has been allowed to evolve for $1.5\,\textrm{Gyr}$. The
purpose of allowing the GALAKOS to evolve first for a short period of time is
to allow for the bar to form unimpacted by the presence of the gas (which
would normally disrupt the formation of the bar). We made one additional
modification when stitching the gas disk together with the N-body disk - we
created a vacuum within the central $4\,\textrm{kpc}$. This vacuum guards
against an initial dramatic infall of gas within the bar region, which we
found to destroy the bar.

>>>>

After generating the gaseous disk in this way, we stitched the gas disk
together with the GALAKOS N-body disk (and bulge and dark matter halo) after
the GALAKOS disk has been allowed to evolve for $1.5\,\textrm{Gyr}$. The
purpose of allowing the GALAKOS disk to evolve first for a short period of
time is to allow for the bar to form unimpacted by the presence of the gas
(which would normally disrupt the formation of the bar). We made one
additional modification when stitching the gas disk together with the N-body
disk - we created a vacuum within the central $4\,\textrm{kpc}$. This vacuum
guards against an initial dramatic infall of gas within the bar region, which
we found to destroy the bar.
